How to Write Theses\\ With Two Line Titles

### 2020-04-13 chapters/results/tables.tex
final draft

\subsection{Rotate}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
\hline
1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
\hline
2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
\hline
3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
\hline
4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
\hline
5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
\hline
6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
\hline
7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
\hline
8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
\hline
9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
\hline
\end{tabular}
\caption{Rotate.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 41.4  & 17.45  & 0  \\
    NN    & 34.8 & 24.75  & 0  \\
    NB    & 30.4 & 42.0 & 0 \\
    SVM   & 40.0 & 29.1 & 0 \\
    KNN   & 47.7  & 20.81 & 0.0 \\
    }\rotate

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=75,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\rotate};
        \addplot table[x=interval,y=Fashion]{\rotate};
        \addplot table[x=interval,y=Letter]{\rotate};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

\subsection{ShiftX}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
     & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
    \hline
    Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
    \hline
    0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
    \hline
        \multirow{3}{*}{1}
            &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
            &-5&5 & -2&1 & & & -6&4 & -9&11\\
            &32&49 & 40&49  & & & 28&49 & 27&49\\
    \hline
    \multirow{2}{*}{2}  
        &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
        & & &   & & -12&6   & & & &\\          
    \hline
    3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
    \hline
    4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
    \hline
    5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
    \hline
    6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
    \hline
    7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
    \hline
    8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
    \hline
    9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
    \hline
\end{tabular}
\caption{ShiftX.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 12.42  & 10.75  & 0  \\
    NN    & 7.83 & 14.71  & 0  \\
    NB    & 9.73 & 22.27 & 0 \\
    SVM   & 11.5 & 11.18 & 0 \\
    KNN   & 14.17  & 9.27 & 0.0 \\
    }\shiftX

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=50,
            ylabel={\Angle},
        ]
        \addplot table[x=interval,y=Digit]{\shiftX};
        \addplot table[x=interval,y=Fashion]{\shiftX};
        \addplot table[x=interval,y=Letter]{\shiftX};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}
MNIST: KNN is the most robust.

\subsection{Shade}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
\hline
1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
\hline
2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
\hline
3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
\hline
4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
\hline
5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
\hline
6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
\hline
7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
\hline
8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
\hline
9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
\hline
\end{tabular}
\caption{Shade.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 64.6  & 55.6  & 0  \\
    NN    & 80.6 & 56.1  & 0  \\
    NB    & 95.5 & 68.63 & 0 \\
    SVM   & 55.2 & 55.8 & 0 \\
    KNN   & 55.0  & 51.9 & 0.0 \\
    }\shade

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\shade};
        \addplot table[x=interval,y=Fashion]{\shade};
        \addplot table[x=interval,y=Letter]{\shade};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

\subsection{Shear}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
\hline
1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
\hline
2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
\hline
3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
\hline
4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
\hline
5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
\hline
6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
\hline
7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
\hline
8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
\hline
9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
\hline
\end{tabular}
\caption{Shear.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 52.4  & 38.82  & 0  \\
    NN    & 41.8 & 41.18  & 0  \\
    NB    & 39.9 & 53.6 & 0 \\
    SVM   & 54.7 & 53.8 & 0 \\
    KNN   & 63.1  & 45.1 & 0.0 \\
    }\shade

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\shade};
        \addplot table[x=interval,y=Fashion]{\shade};
        \addplot table[x=interval,y=Letter]{\shade};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

>>>>

% \subsection{Rotate}
% \begin{table}[ht]
% \centering
% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
% \hline
%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
% \hline
% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
% \hline
% 0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
% \hline
% 1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
% \hline
% 2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
% \hline
% 3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
% \hline
% 4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
% \hline
% 5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
% \hline
% 6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
% \hline
% 7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
% \hline
% 8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
% \hline
% 9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
% \hline
% \end{tabular}
% \caption{Rotate.}
% \label{tbl:test-file-format}
% \end{table}

% \subsubsection{MT: Rotate}
% \pgfplotstableread[row sep=\\,col sep=&]{
%     interval & Digit & Fashion & Letter \\
%     CNN & 75.4 & 39.8 & 43.72 \\
%     NN & 61.6 & 43.36 & 40.59 \\
%     NB & 54.5 & 57.9 & 37.29 \\
%     SVM & 40.0 & 51.5 & 23.153 \\ 
%     KNN & 47.7 & 35.08 & 26.31 \\
%     }\rotate

% \begin{tikzpicture}
%     \begin{axis}[
%             ybar,
%             bar width=.75cm,
%             width=\textwidth,
%             height=.5\textwidth,
%             legend style={at={(0.5,1)},
%                 anchor=north,legend columns=-1},
%             symbolic x coords={CNN,NN,NB,SVM,KNN},
%             xtick=data,
%             nodes near coords,
%             nodes near coords align={vertical},
%             ymin=0,ymax=120,
%             ylabel={Value},
%         ]
%         \addplot table[x=interval,y=Digit]{\rotate};
%         \addplot table[x=interval,y=Fashion]{\rotate};
%         \addplot table[x=interval,y=Letter]{\rotate};
%         \legend{Digit, Fashion, Letter}
%     \end{axis}
% \end{tikzpicture}
\clearpage
When the rotation metamorphic transformation is applied to the MNIST dataset, the convolutional neural-network algorithm has the largest bar. This means that that a larger angle of rotation can be applied to the MNIST dataset before it's accuracy drops below $90\%$ of the original MNIST dataset. Similarly, Naive Bayes is the most robust for Fashion-MNIST datset and KNN is the most robust for EMNIST dataset.

\pgfplotstableread[row sep=\\,col sep=&]{
    Mx & My & Fx & Fy & Ex & Ey \\
    0 & 39 & 0.1 & 13 & 0.2 & 24 \\
    4 & 27 & 4.1 & 19 & 4.2 & 19 \\
    8 & 25 & 8.1 & 19 & 8.2 & 20 \\
    12 & 16 & 12.1 & 18 & 12.2 & 21 \\
    16 & 19 & 16.1 & 15 & 16.2 & 24 \\
    }\mnistx

\pgfplotstableread[row sep=\\,col sep=&]{
   Algo & Mx & My & Fx & Fy & Ex & Ey \\
   CNN & 0 & -34 & 0.1 & -14 & 0.2 & -20 \\
    NN & 4 & -28 & 4.1 & -17 & 4.2 & -18 \\
    NB & 8 & -24 & 8.1 & -19 & 8.2 & -17 \\
    SVM & 12 & -16 & 12.1 & -17 & 12.2 & -20 \\
     KNN & 16 & -18 & 16.1 & -16 & 16.2 & -25 \\
    }\mnisty

\begin{figure}[H]

\begin{tikzpicture}

\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnistx};
\addlegendentry{MNIST}

\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\mnistx};
\addlegendentry{Fashion}

\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\mnistx};
\addlegendentry{EMNIST}

\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnisty};
\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\mnisty};
\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\mnisty};
\end{groupplot}
\end{tikzpicture}
\caption{Robustness graph for rotation property}
\end{figure}

% \subsection{Shade}
% \begin{table}[ht]
% \centering
% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
% \hline
%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
% \hline
% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
% \hline
% 0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
% \hline
% 1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
% \hline
% 2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
% \hline
% 3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
% \hline
% 4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
% \hline
% 5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
% \hline
% 6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
% \hline
% 7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
% \hline
% 8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
% \hline
% 9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
% \hline
% \end{tabular}
% \caption{Shade.}
% \label{tbl:test-file-format}
% \end{table}

% \subsubsection{MT: Shade}
% \pgfplotstableread[row sep=\\,col sep=&]{
%     interval & Digit & Fashion & Letter \\
%     CNN   & 64.6  & 55.6  & 36.76  \\
%     NN    & 80.6 & 56.1  & 74.69  \\
%     NB    & 95.5 & 68.63 & 62.30 \\
%     SVM   & 55.2 & 55.8 & 40.81 \\
%     KNN   & 55.0  & 51.9 & 56.29 \\
%     }\shade

% \begin{tikzpicture}
%     \begin{axis}[
%             ybar,
%             bar width=.75cm,
%             width=\textwidth,
%             height=.5\textwidth,
%             legend style={at={(0.5,1)},
%                 anchor=north,legend columns=-1},
%             symbolic x coords={CNN,NN,NB,SVM,KNN},
%             xtick=data,
%             nodes near coords,
%             nodes near coords align={vertical},
%             ymin=0,ymax=120,
%             ylabel={Value},
%         ]
%         \addplot table[x=interval,y=Digit]{\shade};
%         \addplot table[x=interval,y=Fashion]{\shade};
%         \addplot table[x=interval,y=Letter]{\shade};
%         \legend{Digit, Fashion, Letter}
%     \end{axis}
% \end{tikzpicture}

\pgfplotstableread[row sep=\\,col sep=&]{
    Mx & My & Fx & Fy & Ex & Ey \\
    0 & 55 & 0.1 & 55 & 0.2 & 53 \\
    4 & 69 & 4.1 & 53 & 4.2 & 61 \\
    8 & 96 & 8.1 & 76 & 8.2 & 92 \\
    12 & 52 & 12.1 & 52 & 12.2 & 51 \\
    16 & 51 & 16.1 & 52 & 16.2 & 51 \\
    }\shadex

\pgfplotstableread[row sep=\\,col sep=&]{
   Algo & Mx & My & Fx & Fy & Ex & Ey \\
    CNN & 0 & 0 & 0.1 & 0 & 0.2 & 0 \\
    NN & 4 & 0 & 4.1 & 0 & 4.2 & 0 \\
    NB & 8 & 0 & 8.1 & 0 & 8.2 & 0 \\
    SVM & 12 & 0 & 12.1 & 0 & 12.2 & 0 \\
    KNN & 16 & 0 & 16.1 & 0 & 16.2 & 0 \\
    }\shadey

\begin{figure}[H]
\begin{tikzpicture}
\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.6\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadex};
\addlegendentry{MNIST}

\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shadex};
\addlegendentry{Fashion}

\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shadex};
\addlegendentry{EMNIST}

\nextgroupplot[ybar, width=0.85\textwidth,height=0, bar width=.2cm,yshift=1cm,ymin=0,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shadey}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},ytick=\empty,]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadey};
\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shadey};
\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shadey};

\end{groupplot}
\end{tikzpicture}
\caption{Robustness graph for shading property}
\end{figure}
For the shading metamorphic property we find that Naive Bayes is the most robust algorithm for all the three datasets.

% \subsection{Shear}
% \begin{table}[ht]
% \centering
% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
% \hline
%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
% \hline
% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
% \hline
% 0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
% \hline
% 1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
% \hline
% 2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
% \hline
% 3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
% \hline
% 4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
% \hline
% 5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
% \hline
% 6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
% \hline
% 7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
% \hline
% 8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
% \hline
% 9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
% \hline
% \end{tabular}
% \caption{Shear.}
% \label{tbl:test-file-format}
% \end{table}
\newline

% \subsubsection{MT: Shear}
% \pgfplotstableread[row sep=\\,col sep=&]{
%     interval & Digit & Fashion & Letter \\
%     CNN & 52.4 & 38.81 & 28.84 \\
%     NN  & 41.8 & 41.18 & 28.11 \\
%     NB  & 39.9 & 53.6 & 31.5 \\
%     SVM & 54.7 & 53.8 & 34.84 \\
%     KNN & 63.1 & 45.1 & 38.23 \\
%     }\shear

% \begin{tikzpicture}
%     \begin{axis}[
%             ybar,
%             bar width=.75cm,
%             width=\textwidth,
%             height=.5\textwidth,
%             legend style={at={(0.5,1)},
%                 anchor=north,legend columns=-1},
%             symbolic x coords={CNN,NN,NB,SVM,KNN},
%             xtick=data,
%             nodes near coords,
%             nodes near coords align={vertical},
%             ymin=0,ymax=120,
%             ylabel={Angle},
%         ]
%         \addplot table[x=interval,y=Digit]{\shear};
%         \addplot table[x=interval,y=Fashion]{\shear};
%         \addplot table[x=interval,y=Letter]{\shear};
%         \legend{Digit, Fashion, Letter}
%     \end{axis}
% \end{tikzpicture}
\pgfplotstableread[row sep=\\,col sep=&]{
    Mx & My & Fx & Fy & Ex & Ey \\
    0 & 47 & 0.1 & 24 & 0.2 & 30 \\
    4 & 43 & 4.1 & 29 & 4.2 & 24 \\
    8 & 34 & 8.1 & 33 & 8.2 & 26 \\
    12 & 23 & 12.1 & 31 & 12.2 & 29 \\
    16 & 23 & 16.1 & 29 & 16.2 & 35 \\
    }\shearx

\pgfplotstableread[row sep=\\,col sep=&]{
   Algo & Mx & My & Fx & Fy & Ex & Ey \\
    CNN & 0 & -48 & 0.1 & -25 & 0.2 & -30 \\
    NN & 4 & -46 & 4.1 & -30 & 4.2 & -26 \\
    NB & 8 & -31 & 8.1 & -43 & 8.2 & -23 \\
    SVM & 12 & -28 & 12.1 & -40 & 12.2 & -33 \\
    KNN & 16 & -31 & 16.1 & -32 & 16.2 & -45 \\
    }\sheary

\begin{figure}[H]
\begin{tikzpicture}
\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearx};
\addlegendentry{MNIST}

\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearx};
\addlegendentry{Fashion}

\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearx};
\addlegendentry{EMNIST}

\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\sheary}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\sheary};
\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\sheary};
\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\sheary};

\end{groupplot}
\end{tikzpicture}
\caption{Robustness graph for Shear property}
\end{figure}
For the Shearing property, the convolutional neural-network is the most robust. The Fashion-MNIST and EMNIST datasets have Naive Bayes and KNN as the most robust algorithm respectively.
% \subsection{ShiftX}
% \begin{table}[ht]
% \centering
% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
%     \hline
%      & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
%     \hline
%     Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
%     \hline
%     0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
%     \hline
%         \multirow{3}{*}{1}
%             &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
%             &-5&5 & -2&1 & & & -6&4 & -9&11\\
%             &32&49 & 40&49  & & & 28&49 & 27&49\\
%     \hline
%     \multirow{2}{*}{2}  
%         &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
%         & & &   & & -12&6   & & & &\\          
%     \hline
%     3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
%     \hline
%     4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
%     \hline
%     5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
%     \hline
%     6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
%     \hline
%     7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
%     \hline
%     8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
%     \hline
%     9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
%     \hline
% \end{tabular}
% \caption{ShiftX.}
% \label{tbl:test-file-format}
% \end{table}
\newline

% \subsubsection{MT: ShiftX}
% \pgfplotstableread[row sep=\\,col sep=&]{
%     interval & Digit & Fashion & Letter \\
%     CNN & 11.2 & 5.166666666666667 & 2.892857142857143 \\ 
%     NN & 6.9 & 8.615384615384615 & 2.3214285714285716 \\
%     NB & 8.727272727272727 & 18.0 & 2.5454545454545454 \\
%     SVM & 8.545454545454545 & 7.3076923076923075 & 3.0 \\
%     KNN & 10.416666666666666 & 6.6 & 3.75 \\
%     }\shiftX

% \begin{tikzpicture}
%     \begin{axis}[
%             ybar,
%             bar width=.75cm,
%             width=\textwidth,
%             height=.5\textwidth,
%             legend style={at={(0.5,1)},
%                 anchor=north,legend columns=-1},
%             symbolic x coords={CNN,NN,NB,SVM,KNN},
%             xtick=data,
%             nodes near coords,
%             nodes near coords align={vertical},
%             ymin=0,ymax=50,
%             ylabel={Pixels},
%         ]
%         \addplot table[x=interval,y=Digit]{\shiftX};
%         \addplot table[x=interval,y=Fashion]{\shiftX};
%         \addplot table[x=interval,y=Letter]{\shiftX};
%         \legend{Digit, Fashion, Letter}
%     \end{axis}
% \end{tikzpicture}
\pgfplotstableread[row sep=\\,col sep=&]{
    Mx & My & Fx & Fy & Ex & Ey \\
    0 & 5 & 0.1 & 1 & 0.2 & 1 \\
    4 & 3 & 4.1 & 1 & 4.2 & 1 \\
    8 & 3 & 8.1 & 2 & 8.2 & 1 \\
    12 & 4 & 12.1 & 1 & 12.2 & 1 \\
    16 & 4 & 16.1 & 1 & 16.2 & 1 \\
    }\shearxX

\pgfplotstableread[row sep=\\,col sep=&]{
   Algo & Mx & My & Fx & Fy & Ex & Ey \\
    CNN & 0 & -5 & 0.1 & -1 & 0.2 & -1 \\
    NN & 4 & -3 & 4.1 & -1 & 4.2 & -1 \\
    NB & 8 & -3 & 8.1 & -2 & 8.2 & -1 \\
    SVM & 12 & -4 & 12.1 & -1 & 12.2 & -1 \\
    KNN & 16 & -5 & 16.1 & -1 & 16.2 & -1 \\
    }\shearxY

\begin{figure}[H]
\begin{tikzpicture}
\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.3\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearxX};
\addlegendentry{MNIST}

\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearxX};
\addlegendentry{Fashion}

\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearxX};
\addlegendentry{EMNIST}
